%-------------------------
% Resume in Latex
% Author : Shelby Doolittle
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Shelby Doolittle} & Email : \href{mailto:shelby@shelbyd.com}{shelby@shelbyd.com}\\
  \ & Mobile : +1-804-837-3255 \\
\end{tabular*}


\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Fractal}{Remote (HQ Berlin)}
      {Head of Protocol}{April 2021 - July 2022}
      \resumeItemListStart
        \resumeItem{Protocol}
          {The Fractal Protocol is a greenfield web3 project to improve user data privacy while providing access to that data to websites that did not generate that data. I defined the interface, architecture, and technical operation of the protocol. I was initially hired to be the tech lead for the project, but was promoted to being in charge of the whole project after a few months. I managed a team of 4 people.}
      \resumeItemListEnd

    \resumeSubheading
      {Google}{Pittsburgh, PA}
      {Software Engineer Level 4}{October 2018 - April 2021}
      \resumeItemListStart
        \resumeItem{Shopping Product Curation Tools}
          {Shopping Product Curation Tools builds tools for human operators to manually improve the quality of Google Shopping's product data. I built a task assignment system that processed O(10,000) assignments / day with zero latency from submission to potential assignment. I also designed and built a system to use simple high-scale operator judgements to determine if two retailer offers were for the same product.}
      \resumeItemListEnd

    \resumeSubheading
      {51}{Midlothian, VA}
      {Co-Founder}{January 2017 - Present}
      \resumeItemListStart
        \resumeItem{Interactive Spaces}
          {Interactive Spaces is a suite of software and hardware that allows escape room designers to integrate electronics into their escape rooms easily with previously impossible features included.}
        \resumeItem{Warehouse 29}
          {A VR/Live Action/Escape Room experience. Players fight a sentient AI that has taken over a VR museum dedicated to Edgar Allan Poe. I built all of the VR gameplay and management infrastructure.}
      \resumeItemListEnd

    \resumeSubheading
      {Google}{Mountain View, CA}
      {Software Engineer Level 4}{June 2015 - March 2017}
      \resumeItemListStart
        \resumeItem{OneDiff}
          {OneDiff is a Google internal tool for diffing large batches of structured data. I worked on the frontend visualization, focusing on rendering and presenting \textgreater10GB diffs so that other engineers could understand how their data changed.}
        \resumeItem{Process Consulting}
          {OneDiff was routinely lauded for responsiveness to feedback from internal stakeholders due to my efforts. I was regularly asked to consult on other teams to help improve their process.}
      \resumeItemListEnd

    \resumeSubheading
      {Pivotal Labs}{Mountain View, CA}
      {Software Engineer}{June 2014 - June 2015}
      \resumeItemListStart
        \resumeItem{Samsung Milk Video (Following Feed)}
          {When I joined the Milk Video project, the following feed always had at least 4 engineers triaging defects and performance issues. With dedicated disagreement and straightforward engineering, I was able to dramatically simplify the whole system to zero defects and able to handle new features quickly.}
        \resumeItem{Barnes \& Noble NookPress}
          {Print-on-demand service allowing people to order 1-1000 copies of a custom printed book.}
        \resumeItem{Hawq (Development Tools)}
          {Built CI infrastructure to reduce effort of manual maintenance.}
      \resumeItemListEnd

    \resumeSubheading
      {AgilQuest}{Richmond, VA}
      {Software Engineer}{Oct 2013 - June 2014}
      \resumeItemListStart
        \resumeItem{Forum}
          {Cloud-based booking software for workspaces, and meeting and conference rooms.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Expertise}
  \resumeSubHeadingListStart
    \resumeSubItem{Software Engineering Process}
      {Extreme Programming, Continuous Integration, Continuous Delivery, Pair Programming, Standups, Retrospectives}
    \resumeSubItem{Programming}
      {Algorithms, Data Structures, Web Development, Distributed Systems, Databases}
    \resumeSubItem{Languages}
      {Rust, JavaScript, Java, Ruby, SQL, HTML, CSS, C++, C\#}
    \resumeSubItem{Technologies}
      {Substrate, Angular, PostgreSQL, Rails, Docker, Git, Godot, Unity3D}
    \resumeSubItem{Artificial Intelligence/Machine Learning}
      {Neural Networks, Reinforcement Learning, Genetic Algorithms, Keras}
    \resumeSubItem{Blockchains}
      {Cryptography, Bitcoin, Blockchains}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
